Use the IEEE numbered reference style for referencing your work as shown in your thesis guidelines.
Please remember that the majority of your referenced work should be from journal articles, technical
reports and books not online sources such as Wikipedia.

\begin{thebibliography}{5}
\bibitem{smt2011} M. S. Tsoeu and M. Braae, ``Control Systems,'' \emph{IEEE}, {\bf vol. 34(3)}, pp. 123-129, 2011.
\bibitem{jct2010} J. C. Tapson, \emph{Instrumentation}, UCT Press, Cape Town, 2010.

\bibitem{nonContact2017} A. Adikari, N. Ganegoda and W. Wanniarachchi, "Non-Contact human body parameter measurement based on Kinect Sensor," \emph{IOSR Journal of Computer Engineering}, vol. 19, no. 3, pp. 80-85, 2017. 

\bibitem{handDetection2015} M. Karbasi, Z. Bhatti, P. Nooralishahi, A. Shah and S. Mazloomnezhad. (2015). Real-Time hands detection in depth image by using distance with Kinect Camera. \emph{International Journal of Internet of Things}. [Online]. Available: http://article.sapub.org/10.5923.c.ijit.201501.01.html

\bibitem{virtualDress2012} F. Isikdogan and G. Kara, "A real time virtual dressing room application using Kinect," Bogazici University, Istanbul, 2012.

\bibitem{kinectComp2011} S. Zennaro, M. Munaro, S. Milani, P. Zanuttigh, A. Bernardi, S. Ghidoni and E. Menegatti. (2015) Performance evaluation of the 1st and 2nd generation Kinect for multimedia applications. \emph{IEEE}, [Online]. Available: https://doi.org/10.1109/ICME.2015.7177380

\bibitem{msdnKinectSpecs2017} Microsoft Developer Network, "Kinect for Windows Sensor Components and Specifications," [Online]. Available: https://msdn.microsoft.com/en-us/library/jj131033.aspx. [Accessed 31 10 2017].

\bibitem{msdnDepthCamKinect2017} Microsoft Developer Network, "Depth Camera," [Online]. Available: https://msdn.microsoft.com/en-us/library/hh438997.aspx. [Accessed 31 10 2017].

\bibitem{msdnCoSpaces2017} Microsoft Developer Network, "Coordinate Spaces," [Online]. Available: https://msdn.microsoft.com/en-us/library/hh973078.aspx\#Depth\_Ranges. [Accessed 31 10 2017].

\bibitem{msdnSkelTrack2017} Microsoft Developer Network, "Skeletal Tracking," [Online]. Available: https://msdn.microsoft.com/en-us/library/hh973074.aspx. [Accessed 31 10 2017].

\bibitem{msdnTrackUserSkel2017} Microsoft Developer Network, "Tracking Users with Kinect Skeletal Tracking," [Online]. Available: https://msdn.microsoft.com/en-us/library/jj131025.aspx. [Accessed 31 10 2017].
\end{thebibliography}
